Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex
pass on example

\sloppy
\vspace{1ex}\noindent\textbf{Issue \#4,
  Table~\Fix{XX}.}  The code snippet below show a bug
in \chakra{}.

@@

\vspace{1ex}\noindent\textbf{Issue \#16, Table~\Fix{XX}}.
\Igor{
  Este foi caso de bug confirmado que foi manifestado no engenho \veight{}.
  Este test case oriundo da suite Test262 foi fuzzado pelo \quickfuzz{}
  que por ser um fuzzer mutacional, usa uma gramatica \js{} que auxilia na geracao
  de entradas validas. In Figure~\ref{fig:bug-veight}, we observed a \CodeIn{eval} statement
  that try to evaluate a \CodeIn{function f()}, this test case specify the ecma spec
  B.3.3.3~\cite{spec-b333} that describe an evaluation of a block statement in eval code containing a 
  function declaration. The fuzzer removes the function declaration and 
  injects a function with a break statement outside a loop. According to specification~\cite{break-statement},
  the break statement should throw an early error (in this case a SyntaxError) 
  if the break statement is not nested in an iterational or a switch statement. All engines works
  as expected but \veight{} pass without failures.
}

\begin{figure}[h!]
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assert, assertEq, var, yield, in, function, eval,
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}
// Original file
eval(
"{ 
    function f() { 
      return 'declaration'; 
    } 
 }
 assert.sameValue(typeof f, 'function');
 \assert.sameValue(f(), 'declaration');"
);
// Fuzzed file
eval(function b (a) {
  break;
});
  \end{lstlisting}
  \normalsize
  \caption{\label{fig:bug-veight}Fuzzed code mutated by \quickfuzz{}
  and reported in \veight{} engine}
\end{figure}

>>>>

\sloppy
\vspace{1ex}\noindent\textbf{Issue \#4, Table~\Fix{XX}.} The code
snippet below shows the test input we used to reveal a bug in
\chakra.

@@

\vspace{1ex}\noindent\textbf{Issue \#16, Table~\Fix{XX}}.  The code
snippet below shows the test input we used to reveal a bug in \veight.

%% eval(
%% "{ 
%%     function f() { 
%%       return 'declaration'; 
%%     } 
%%  }
%%  assert.sameValue(typeof f, 'function');
%%  \assert.sameValue(f(), 'declaration');"
%% );
%% // Fuzzed file

\begin{figure}[h!]
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assert, assertEq, var, yield, in, function, eval,
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}
eval(function b (a) {
  break;
});
  \end{lstlisting}
  \normalsize
  %% \caption{\label{fig:bug-veight}Fuzzed code mutated by \quickfuzz{}
  %% and reported in \veight{} engine}
\end{figure}

This code snippet was obtained by fuzzing a Test262 test with
\quickfuzz. In its original version, a string (omitted for space),
passed as argument to the \CodeIn{eval} function, encoded the actual
test. The fuzzer replaced the string argument with a function whose
body is a \CodeIn{break} statement outside a valid block
statement. Section B.3.3.3 from the spec~\cite{spec-b333} documents
how eval should be handle code containing a function declaration.
According to specification~\cite{break-statement}, the break statement
should throw an early error--in this case a SyntaxError--if the break
statement is not nested in an iterational or a switch statement. In
this case, all engines behave as expected but \veight{} pass without
failures.

%% \Igor{
%%   Este foi caso de bug confirmado que foi manifestado no engenho \veight{}.
%%   Este test case oriundo da suite Test262 foi fuzzado pelo \quickfuzz{}
%%   que por ser um fuzzer mutacional, usa uma gramatica \js{} que auxilia na geracao
%%   de entradas validas. In Figure~\ref{fig:bug-veight}, we observed a \CodeIn{eval} statement
%%   that try to evaluate a \CodeIn{function f()}, this test case specify the ecma spec
%%   B.3.3.3~\cite{spec-b333} that describe an evaluation of a block statement in eval code containing a 
%%   function declaration. The fuzzer removes the function declaration and 
%%   injects a function with a break statement outside a loop. According to specification~\cite{break-statement},
%%   the break statement should throw an early error (in this case a SyntaxError) 
%%   if the break statement is not nested in an iterational or a switch statement. All engines works
%%   as expected but \veight{} pass without failures.
%% }
